Appendix B: Exploratory LPA for Ocean Microplastics

### 2023-01-24 appendix_b.tex
revert MGV previous commit

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Load required packages}
\FunctionTok{library}\NormalTok{(tidySEM) }
\FunctionTok{library}\NormalTok{(ggplot2)}
\CommentTok{\# Load data}
\NormalTok{df\_analyze }\OtherTok{\textless{}{-}}\NormalTok{ alkema\_microplastics[alkema\_microplastics}\SpecialCharTok{$}\NormalTok{category }\SpecialCharTok{==} \StringTok{"Fragment"}\NormalTok{, ]}
\NormalTok{df }\OtherTok{\textless{}{-}}\NormalTok{ df\_analyze[ ,}\FunctionTok{c}\NormalTok{(}\StringTok{"length"}\NormalTok{, }\StringTok{"width"}\NormalTok{)]}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{desc }\OtherTok{\textless{}{-}}\NormalTok{ tidySEM}\SpecialCharTok{::}\FunctionTok{descriptives}\NormalTok{(df)}
\NormalTok{desc }\OtherTok{\textless{}{-}}\NormalTok{ desc[, }\FunctionTok{c}\NormalTok{(}\StringTok{"name"}\NormalTok{, }\StringTok{"type"}\NormalTok{, }\StringTok{"n"}\NormalTok{, }\StringTok{"missing"}\NormalTok{, }\StringTok{"unique"}\NormalTok{, }
\StringTok{"mean"}\NormalTok{, }\StringTok{"median"}\NormalTok{, }\StringTok{"sd"}\NormalTok{, }\StringTok{"min"}\NormalTok{, }\StringTok{"max"}\NormalTok{, }\StringTok{"skew\_2se"}\NormalTok{, }\StringTok{"kurt\_2se"}\NormalTok{)]}
\NormalTok{papaja}\SpecialCharTok{::}\FunctionTok{apa\_table}\NormalTok{(desc, }\AttributeTok{caption =} \StringTok{"Descriptive statistics"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{df\_plot}\SpecialCharTok{$}\NormalTok{Value }\OtherTok{\textless{}{-}} \FunctionTok{log}\NormalTok{(df\_plot}\SpecialCharTok{$}\NormalTok{Value)}
\FunctionTok{ggplot}\NormalTok{(df\_plot, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ Value)) }\SpecialCharTok{+}
  \FunctionTok{geom\_density}\NormalTok{() }\SpecialCharTok{+}
  \FunctionTok{facet\_wrap}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{Variable)}\SpecialCharTok{+}
  \FunctionTok{theme\_bw}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{df }\OtherTok{\textless{}{-}} \FunctionTok{reshape}\NormalTok{(df\_plot, }\AttributeTok{direction =} \StringTok{"wide"}\NormalTok{, }\AttributeTok{v.names =} \StringTok{"Value"}\NormalTok{)[, }\SpecialCharTok{{-}}\DecValTok{1}\NormalTok{]}
\FunctionTok{names}\NormalTok{(df) }\OtherTok{\textless{}{-}} \FunctionTok{gsub}\NormalTok{(}\StringTok{"Value."}\NormalTok{, }\StringTok{""}\NormalTok{, }\FunctionTok{names}\NormalTok{(df), }\AttributeTok{fixed =} \ConstantTok{TRUE}\NormalTok{)}
\FunctionTok{ggplot}\NormalTok{(df, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ length, }\AttributeTok{y =}\NormalTok{ width)) }\SpecialCharTok{+}
  \FunctionTok{geom\_point}\NormalTok{(}\AttributeTok{alpha =}\NormalTok{ .}\DecValTok{1}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{theme\_bw}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{set.seed}\NormalTok{(}\DecValTok{123}\NormalTok{)}
\NormalTok{res }\OtherTok{\textless{}{-}} \FunctionTok{mx\_profiles}\NormalTok{(}\AttributeTok{data =}\NormalTok{ df,}
                   \AttributeTok{classes =} \DecValTok{1}\SpecialCharTok{:}\DecValTok{4}\NormalTok{,}
                   \AttributeTok{variances =} \FunctionTok{c}\NormalTok{(}\StringTok{"equal"}\NormalTok{, }\StringTok{"varying"}\NormalTok{),}
                   \AttributeTok{covariances =} \FunctionTok{c}\NormalTok{(}\StringTok{"zero"}\NormalTok{, }\StringTok{"equal"}\NormalTok{,}
                                   \StringTok{"varying"}\NormalTok{),}
                   \AttributeTok{expand\_grid =} \ConstantTok{TRUE}\NormalTok{)}
\FunctionTok{saveRDS}\NormalTok{(res, }\StringTok{"res\_gmm.RData"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{fit}\SpecialCharTok{$}\NormalTok{par\_ratio }\OtherTok{\textless{}{-}}\NormalTok{ (}\DecValTok{5605}\SpecialCharTok{*}\NormalTok{fit}\SpecialCharTok{$}\NormalTok{n\_min) }\SpecialCharTok{/}\NormalTok{ (fit}\SpecialCharTok{$}\NormalTok{Parameters}\SpecialCharTok{/}\NormalTok{fit}\SpecialCharTok{$}\NormalTok{Classes)}
\NormalTok{fit[ , }\FunctionTok{c}\NormalTok{(}\StringTok{"Name"}\NormalTok{, }\StringTok{"LL"}\NormalTok{, }\StringTok{"Parameters"}\NormalTok{, }\StringTok{"par\_ratio"}\NormalTok{,}
         \StringTok{"BIC"}\NormalTok{, }\StringTok{"Entropy"}\NormalTok{,}
         \StringTok{"prob\_min"}\NormalTok{, }\StringTok{"prob\_max"}\NormalTok{, }
         \StringTok{"n\_min"}\NormalTok{, }\StringTok{"n\_max"}\NormalTok{,}
         \StringTok{"lmr\_p"}\NormalTok{)]}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{fit }\OtherTok{\textless{}{-}}\NormalTok{ fit[}\SpecialCharTok{!}\NormalTok{fit}\SpecialCharTok{$}\NormalTok{n\_min }\SpecialCharTok{\textless{}}\NormalTok{ .}\DecValTok{1}\NormalTok{, ]}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{plot}\NormalTok{(fit) }\SpecialCharTok{+} \FunctionTok{theme}\NormalTok{(}\AttributeTok{axis.text.x =} \FunctionTok{element\_text}\NormalTok{(}\AttributeTok{angle =} \DecValTok{90}\NormalTok{, }\AttributeTok{vjust =} \FloatTok{0.5}\NormalTok{, }\AttributeTok{hjust=}\DecValTok{1}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{res\_bic }\OtherTok{\textless{}{-}}\NormalTok{ res[[}\StringTok{"free var, free cov 2"}\NormalTok{]]}
\NormalTok{cp }\OtherTok{\textless{}{-}} \FunctionTok{class\_prob}\NormalTok{(res\_bic)}
\NormalTok{results }\OtherTok{\textless{}{-}} \FunctionTok{table\_results}\NormalTok{(res\_bic, }\AttributeTok{columns =} \FunctionTok{c}\NormalTok{(}\StringTok{"label"}\NormalTok{, }\StringTok{"est"}\NormalTok{, }\StringTok{"std\_est"}\NormalTok{))}
\NormalTok{results}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{df\_pt }\OtherTok{\textless{}{-}} \FunctionTok{mx\_dummies}\NormalTok{(df\_analyze}\SpecialCharTok{$}\NormalTok{poly\_type)}
\NormalTok{aux\_pt }\OtherTok{\textless{}{-}} \FunctionTok{BCH}\NormalTok{(res\_bic, }\AttributeTok{model =} \StringTok{"poly\_typeOther | t1}
\StringTok{                                poly\_typePE | t1}
\StringTok{                                poly\_typePP | t1"}\NormalTok{, }\AttributeTok{data =}\NormalTok{ df\_pt)}
\NormalTok{aux\_pt }\OtherTok{\textless{}{-}} \FunctionTok{mxTryHardOrdinal}\NormalTok{(aux\_pt)}
\end{Highlighting}
\end{Shaded}

>>>>

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Load required packages}
\FunctionTok{library}\NormalTok{(tidySEM)}
\FunctionTok{library}\NormalTok{(ggplot2)}
\CommentTok{\# Load data}
\NormalTok{df\_analyze }\OtherTok{\textless{}{-}}\NormalTok{ alkema\_microplastics[alkema\_microplastics}\SpecialCharTok{$}\NormalTok{category }\SpecialCharTok{==}
    \StringTok{"Fragment"}\NormalTok{, ]}
\NormalTok{df }\OtherTok{\textless{}{-}}\NormalTok{ df\_analyze[, }\FunctionTok{c}\NormalTok{(}\StringTok{"length"}\NormalTok{, }\StringTok{"width"}\NormalTok{)]}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{desc }\OtherTok{\textless{}{-}}\NormalTok{ tidySEM}\SpecialCharTok{::}\FunctionTok{descriptives}\NormalTok{(df)}
\NormalTok{desc }\OtherTok{\textless{}{-}}\NormalTok{ desc[, }\FunctionTok{c}\NormalTok{(}\StringTok{"name"}\NormalTok{, }\StringTok{"type"}\NormalTok{, }\StringTok{"n"}\NormalTok{, }\StringTok{"missing"}\NormalTok{, }\StringTok{"unique"}\NormalTok{, }\StringTok{"mean"}\NormalTok{,}
    \StringTok{"median"}\NormalTok{, }\StringTok{"sd"}\NormalTok{, }\StringTok{"min"}\NormalTok{, }\StringTok{"max"}\NormalTok{, }\StringTok{"skew\_2se"}\NormalTok{, }\StringTok{"kurt\_2se"}\NormalTok{)]}
\NormalTok{papaja}\SpecialCharTok{::}\FunctionTok{apa\_table}\NormalTok{(desc, }\AttributeTok{caption =} \StringTok{"Descriptive statistics"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{df\_plot}\SpecialCharTok{$}\NormalTok{Value }\OtherTok{\textless{}{-}} \FunctionTok{log}\NormalTok{(df\_plot}\SpecialCharTok{$}\NormalTok{Value)}
\FunctionTok{ggplot}\NormalTok{(df\_plot, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ Value)) }\SpecialCharTok{+} \FunctionTok{geom\_density}\NormalTok{() }\SpecialCharTok{+} \FunctionTok{facet\_wrap}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{Variable) }\SpecialCharTok{+}
    \FunctionTok{theme\_bw}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{df }\OtherTok{\textless{}{-}} \FunctionTok{reshape}\NormalTok{(df\_plot, }\AttributeTok{direction =} \StringTok{"wide"}\NormalTok{, }\AttributeTok{v.names =} \StringTok{"Value"}\NormalTok{)[,}
    \SpecialCharTok{{-}}\DecValTok{1}\NormalTok{]}
\FunctionTok{names}\NormalTok{(df) }\OtherTok{\textless{}{-}} \FunctionTok{gsub}\NormalTok{(}\StringTok{"Value."}\NormalTok{, }\StringTok{""}\NormalTok{, }\FunctionTok{names}\NormalTok{(df), }\AttributeTok{fixed =} \ConstantTok{TRUE}\NormalTok{)}
\FunctionTok{ggplot}\NormalTok{(df, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ length, }\AttributeTok{y =}\NormalTok{ width)) }\SpecialCharTok{+} \FunctionTok{geom\_point}\NormalTok{(}\AttributeTok{alpha =} \FloatTok{0.1}\NormalTok{) }\SpecialCharTok{+}
    \FunctionTok{theme\_bw}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{set.seed}\NormalTok{(}\DecValTok{123}\NormalTok{)}
\NormalTok{res }\OtherTok{\textless{}{-}} \FunctionTok{mx\_profiles}\NormalTok{(}\AttributeTok{data =}\NormalTok{ df, }\AttributeTok{classes =} \DecValTok{1}\SpecialCharTok{:}\DecValTok{4}\NormalTok{, }\AttributeTok{variances =} \FunctionTok{c}\NormalTok{(}\StringTok{"equal"}\NormalTok{,}
    \StringTok{"varying"}\NormalTok{), }\AttributeTok{covariances =} \FunctionTok{c}\NormalTok{(}\StringTok{"zero"}\NormalTok{, }\StringTok{"equal"}\NormalTok{, }\StringTok{"varying"}\NormalTok{),}
    \AttributeTok{expand\_grid =} \ConstantTok{TRUE}\NormalTok{)}
\FunctionTok{saveRDS}\NormalTok{(res, }\StringTok{"res\_gmm.RData"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{fit}\SpecialCharTok{$}\NormalTok{par\_ratio }\OtherTok{\textless{}{-}}\NormalTok{ (}\DecValTok{5605} \SpecialCharTok{*}\NormalTok{ fit}\SpecialCharTok{$}\NormalTok{n\_min)}\SpecialCharTok{/}\NormalTok{(fit}\SpecialCharTok{$}\NormalTok{Parameters}\SpecialCharTok{/}\NormalTok{fit}\SpecialCharTok{$}\NormalTok{Classes)}
\NormalTok{fit[, }\FunctionTok{c}\NormalTok{(}\StringTok{"Name"}\NormalTok{, }\StringTok{"LL"}\NormalTok{, }\StringTok{"Parameters"}\NormalTok{, }\StringTok{"par\_ratio"}\NormalTok{, }\StringTok{"BIC"}\NormalTok{, }\StringTok{"Entropy"}\NormalTok{,}
    \StringTok{"prob\_min"}\NormalTok{, }\StringTok{"prob\_max"}\NormalTok{, }\StringTok{"n\_min"}\NormalTok{, }\StringTok{"n\_max"}\NormalTok{, }\StringTok{"lmr\_p"}\NormalTok{)]}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{fit }\OtherTok{\textless{}{-}}\NormalTok{ fit[}\SpecialCharTok{!}\NormalTok{fit}\SpecialCharTok{$}\NormalTok{n\_min }\SpecialCharTok{\textless{}} \FloatTok{0.1}\NormalTok{, ]}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{plot}\NormalTok{(fit) }\SpecialCharTok{+} \FunctionTok{theme}\NormalTok{(}\AttributeTok{axis.text.x =} \FunctionTok{element\_text}\NormalTok{(}\AttributeTok{angle =} \DecValTok{90}\NormalTok{, }\AttributeTok{vjust =} \FloatTok{0.5}\NormalTok{,}
    \AttributeTok{hjust =} \DecValTok{1}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{res\_bic }\OtherTok{\textless{}{-}}\NormalTok{ res[[}\StringTok{"free var, free cov 2"}\NormalTok{]]}
\NormalTok{cp }\OtherTok{\textless{}{-}} \FunctionTok{class\_prob}\NormalTok{(res\_bic)}
\NormalTok{results }\OtherTok{\textless{}{-}} \FunctionTok{table\_results}\NormalTok{(res\_bic, }\AttributeTok{columns =} \FunctionTok{c}\NormalTok{(}\StringTok{"label"}\NormalTok{, }\StringTok{"est"}\NormalTok{,}
    \StringTok{"std\_est"}\NormalTok{))}
\NormalTok{results}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{df\_pt }\OtherTok{\textless{}{-}} \FunctionTok{mx\_dummies}\NormalTok{(df\_analyze}\SpecialCharTok{$}\NormalTok{poly\_type)}
\NormalTok{aux\_pt }\OtherTok{\textless{}{-}} \FunctionTok{BCH}\NormalTok{(res\_bic, mo}
\AttributeTok{l =} \StringTok{"poly\_typeOther | t1}
\StringTok{                                poly\_typePE | t1}
\StringTok{                                poly\_typePP | t1"}\NormalTok{,}
    \AttributeTok{data =}\NormalTok{ df\_pt)}
\NormalTok{aux\_pt }\OtherTok{\textless{}{-}} \FunctionTok{mxTryHardOrdinal}\NormalTok{(aux\_pt)}
\end{Highlighting}
\end{Shaded}
